% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
\usepackage{hyperref}
\hypersetup{colorlinks=true,urlcolor=blue}

% Center align address.  See http://tex.stackexchange.com/questions/94204/using-the-res-cls-latex-file-how-do-i-centre-the-address
\makeatletter
\def\@tablebox#1{\begin{tabular}[t]{@{}c@{\extracolsep{\fill}}}#1\end{tabular}}
\makeatother


\begin{document}

\name{Mark Tozzi}

\address{Baltimore, MD $\bullet$ (917) 678 3636 \\
\href{mailto:mark.tozzi@gmail.com}{mark.tozzi@gmail.com}
$\bullet$ GitHub: \href{https://github.com/not-napoleon}{not-napoleon}
}


\begin{resume}

\section{Summary}
I am a software engineer with two decades of experience, most of it working
fully remote, in the data engineering space.  My recent work has been in
information retrieval, with a focus on metric analytic queries. I have worked in
most phases of data processing operations, including building ETL pipelines,
logs to metrics work, application monitoring, and machine learning. I love 
solving hard problems and finding ways to make data available to users in a 
meaningful way.

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Software \& \\ Languages}
   \begin{tabular}{l p{3in}}
     \underline{Languages:} & Java, Python, SQL, Shell scripting \\
     \underline{Data storage and processing:} & Elasticsearch, Lucene, Postgres, Kafka, Redis \\
     \underline{Other Tools:} & Cursor AI, Eclipse MAT
   \end{tabular}

\raggedright{}
\section{Experience}
{\bf Senior Developer (Remote)} \\
    Elasticsearch B.V. \hfill 2018--2026
    \begin{itemize}
        \item Worked as a Java developer on Elasticsearch, a distributed search
            engine, with a focus on logs and metrics query processing and optimization. 
        \item My work included developing new aggregations, supporting new data types,
            query optimization, and addressing customer issues.
        \item Used approximate data structures, like Hyper-Log-Log and T-Digest,
            to build efficient statistical aggregations.
        \item Worked on developing a new query language, ESQL, and supporting
            compute layer, including logical and physical layer optimization rules.
        \item Used JUnit parametrized testing to build out a robust randomized
            testing framework for ESQL scalar functions, which was used as the
            model for later testing.
        \item Elasticsearch is open source.  My work was done mostly
            \href{https://github.com/elastic/elasticsearch/pulls?q=is%3Apr+author%3Anot-napoleon+is%3Aclosed}{in
            the open}.  I also reviewed and merged community PRs as needed.
        \item Served as the Elasticsearch team point of contact for our merger
            with Optimyze, helping them move the application onto the Elastic
            stack.
        \item Responded to production incidents and support escalations in Elastic's managed cloud, 
            as part of a 24/7 on call rotation.
        \item Investigated and resolved customer issues, including performance 
            degradation issues and out of memory errors.
        \item Wrote and reviewed technical design documents as part of a 
            cross team collaboration process.
        \item Mentored new hires and other co-workers as part of a formal 
            mentoring program.
        \item Wrote detailed JavaDoc and internal documentation which was used
            by other developers as AI Agent formulas for complex coding tasks.
        \item Published a
            \href{https://www.elastic.co/blog/how-elastic-traced-a-formatting-bug-in-elasticsearch}{technical blog
            post} detailing a deep dive into debugging a date formatting bug in Java.
        \item Used Elastic's custom benchmarking tool (\href{https://github.com/elastic/rally}{rally})
            to performance test changes and investigate regressions.
        \item Worked closely with Product Management team to plan, scope, and
            estimate features.
    \end{itemize}
{\bf Platform Developer (Remote)}\\
    Rocana, Inc.\hfill 2015--2017
\begin{itemize}
    \item Worked on distributed full text search system using time sharded
        Lucene indexes stored in HDFS.
    \item Built and debugged ETL pipeline to ingest records from Kafka
        and index them into Lucene.
    \item Worked with documentation team lead to produce both customer facing
        and internal documentation for every release.
    \item Used both code analysis and log analysis techniques to debug subtle
        threading issues in highly multi-threaded, callback based, architecture.
    \item Worked with customer support to resolve tier 3 escalations, and
        communicate with customers.
\end{itemize}

{\bf Senior Developer (Remote)}\\
    Keep.com (Part of Keep Holdings, Inc) \hfill 2012--2015
\begin{itemize}
  \item Initiated web crawler project and grew it to a team of 4, crawling
    over 1 million pages twice a day, using Celery and Flask to manage job
    requests and returning data.
  \item Built machine learning models and web scraping tools using
    scikit-learn and beautiful soup to analyze and extract information from
    retailer websites and emails.
  \item Led successful effort to integrate Etsy's Statsd system as a central
    broker for tracking internal metrics.
  \item Migrated from pure Redis backend to hybrid Redis/Postgres backend,
      with no data loss and minimal downtime.
  \item Practiced Test Driven Development (TDD) to dramatically lower the
      defect rate in released code.  Converted several other team members to
      the TDD methodology.
  \item Mentored team members in code style and design.
\end{itemize}

{\bf Senior Analytics Engineer (Remote)}\\
Adkeeper Networks (Part of Keep Holdings, Inc) \hfill  2010--2012
\begin{itemize}
  \item Built batch processing analytics system based on Hadoop, using Pig
      scripts for ETL operations.
  \item Maintained suite of JUnit-based integration tests for import and
      export of data.
  \item Diagnosed and helped to solve operational problems with delivery of
      tens of gigabytes of log data from several systems.
\end{itemize}

{\bf Developer}\\
About.com, New York, NY \hfill  2006--2010
\begin{itemize}
  \item Supported a site usage tracking system which processed
    over 60 Gigabytes of data daily from 90 servers in 3 data centers.
  \item Designed and implemented a new metrics system using the Apache
    Hadoop framework, Apache Hive, and MapReduce to feed data into a MySQL data
    warehouse.
  \item Supported over 600 users across three divisions.
\end{itemize}

\section{Education}
Bachelor of Science in Computer Science, Polytechnic University, Brooklyn, New
York, 2003

\end{resume}
\end{document}
